Towards Reliable Machine Learning Deployments in the Cloud

### 2023-12-13 plots/cifar/aft_comparison.tex
update plots

\begin{table}
\caption{Comparison of AFR Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -472.03 & 0.83 & -472.03 & 0.25 & 0.22 \\
cox & -- & 0.83 & -- & 0.20 & 0.25 \\
log_logistic & -514.66 & 0.83 & -514.66 & 0.25 & 0.21 \\
log_normal & -518.86 & 0.83 & -518.86 & 0.26 & 0.22 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{Comparison of AFR Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -550 & 0.856 & -550 & 0.266 & 0.219 \\
cox & -- & 0.856 & -- & 0.202 & 0.254 \\
log_logistic & -562 & 0.857 & -562 & 0.258 & 0.215 \\
log_normal & -568 & 0.857 & -568 & 0.258 & 0.216 \\
\bottomrule
\end{tabular}
\end{table}

### 2023-12-13 plots/cifar100/aft_comparison.tex
update plots

\begin{table}
\caption{Comparison of AFR Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -329.38 & 0.83 & -329.38 & 0.33 & 0.18 \\
cox & -- & 0.84 & -- & 0.24 & 0.16 \\
log_logistic & -353.45 & 0.84 & -353.45 & 0.31 & 0.17 \\
log_normal & -355.45 & 0.84 & -355.45 & 0.31 & 0.17 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{Comparison of AFR Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -361 & 0.845 & -361 & 0.331 & 0.179 \\
cox & -- & 0.847 & -- & 0.238 & 0.162 \\
log_logistic & -371 & 0.852 & -371 & 0.318 & 0.172 \\
log_normal & -372 & 0.851 & -372 & 0.313 & 0.174 \\
\bottomrule
\end{tabular}
\end{table}

### 2023-12-13 plots/combined/aft_comparison.tex
update plots

\begin{table}
\caption{Comparison of AFR Models on the COMBINED dataset.}
\label{tab:Combined}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -4732.34 & 0.82 & -4732.34 & 0.00 & 0.00 \\
cox & -- & 0.82 & -- & 0.00 & 0.00 \\
log_logistic & -4770.78 & 0.81 & -4770.78 & 0.00 & 0.00 \\
log_normal & -4788.03 & 0.81 & -4788.03 & 0.00 & 0.00 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{Comparison of AFR Models on the COMBINED dataset.}
\label{tab:Combined}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -6.36e+03 & 0.834 & -6.36e+03 & 0.00258 & 0.00195 \\
cox & -- & 0.847 & -- & 0.00224 & 0.00199 \\
log_logistic & -6.62e+03 & 0.862 & -6.62e+03 & 0.00274 & 0.00189 \\
log_normal & -6.6e+03 & 0.862 & -6.6e+03 & 0.0027 & 0.00186 \\
\bottomrule
\end{tabular}
\end{table}

### 2023-12-13 plots/mnist/aft_comparison.tex
update plots

\begin{table}
\caption{Comparison of AFR Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -606.12 & 0.78 & -606.12 & 0.23 & 0.22 \\
cox & -- & 0.78 & -- & 0.18 & 0.22 \\
log_logistic & -606.18 & 0.78 & -606.18 & 0.22 & 0.22 \\
log_normal & -616.30 & 0.78 & -616.30 & 0.23 & 0.22 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{Comparison of AFR Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -778 & 0.886 & -778 & 0.238 & 0.204 \\
cox & -- & 0.888 & -- & 0.185 & 0.201 \\
log_logistic & -759 & 0.884 & -759 & 0.226 & 0.204 \\
log_normal & -752 & 0.881 & -752 & 0.225 & 0.202 \\
\bottomrule
\end{tabular}
\end{table}
